Comparison of Catalogs

### 2024-07-25 compare/compare.qmd
added % of clipped data

        # fit the data with the fitter
        # check if sigma
        if sigma is False:
            fitted_line = fit(line_init, x_data, y_data)
            outliers = None
        else:
            or_fit = fitting.FittingWithOutlierRemoval(fit, sigma_clip, niter=3, sigma=2)
            fitted_line, outliers = or_fit(line_init, x_data, y_data)
        slope = fitted_line.slope.value
        intercept = fitted_line.intercept.value

@@

    # Plot the data with error bars
    # errorbar -> needs np.ma -> no units
    if outliers is not None:
        filtered_data = np.ma.masked_array(y_data, mask = outliers)
        plt.errorbar(x_data, y_data, yerr=yerr_d, c = "black", label="Clipped Data", fmt = "o", fillstyle = "none")
        plt.scatter(x_data, filtered_data,  label="Fitted Data", c = "blue")
    else:
        plt.errorbar(x_data, y_data, xerr = xerr_d, yerr = yerr_d, alpha = 0.3, c = "blue", label = "Data", fmt = ".")

@@

|  LCV  | HECATE |   Description   | Pearson Correlation \[-1,1\] |
|:-----:|:------:|:---------------:|:----------------------------:|
| Ra_1  |  RA_2  | Right Ascension |      `{python} ra_corr`      |
| Dec_1 | DEC_2  |   Declination   |     `{python} dec_corr`      |
|  Dis  |   D    |    Distance     |      `{python} d_corr`       |

scatter_plot(dt["Ra_1"], dt["RA_2"]), scatter_plot(dt["Dec_1"], dt["DEC_2"]), scatter_plot(dt["Dis"], dt["D"])
```

## Velocities

>>>>

        # fit the data with the fitter
        # check if sigma
        if sigma is False:
            fitted_line = fit(line_init, x_data, y_data)
            outliers = None
        else:
            or_fit = fitting.FittingWithOutlierRemoval(fit, sigma_clip, niter =3, sigma=3)
            fitted_line, outliers = or_fit(line_init, x_data, y_data)
        slope = fitted_line.slope.value
        intercept = fitted_line.intercept.value

@@

    # Plot the data with error bars
    # errorbar -> needs np.ma -> no units
    if outliers is not None:
        filtered_data = np.ma.masked_array(y.value , mask = outliers)
        outlier_percentage = (np.sum(outliers) / len(outliers)) * 100

        plt.errorbar(x.value, y.value, yerr=yerr_d, c = "black", label="Clipped Data, {} ({}%)".format(np.sum(outliers), round(outlier_percentage,1)), fmt = "o", fillstyle = "none")
        plt.scatter(x[~outliers], y[~outliers],  label=f"Fitted Data, {np.sum(~filtered_data.mask)}", c = "blue")

    else:
        plt.errorbar(x_data, y_data, xerr = xerr_d, yerr = yerr_d, alpha = 0.3, c = "blue", label = "Data", fmt = ".")

@@

|  LCV  | HECATE |   Description   | Pearson Correlation \[-1,1\] |
|:-----:|:------:|:---------------:|:----------------------------:|
| Ra_1  |  RA_2  | Right Ascension |      `{python} ra_corr`      |
| Dec_1 | DEC_2  |   Declination   |     `{python} dec_corr`      |
|  Dis  |   D    |    Distance     |      `{python} d_corr`       |
::: panel-tabset
## Right Ascnsion
```{python}

scatter_plot(dt["Ra_1"], dt["RA_2"])
```
## Declination
```{python}
scatter_plot(dt["Dec_1"], dt["DEC_2"]), 
```
## Distance
```{python}
scatter_plot(dt["Dis"], dt["D"])
```
:::
## Velocities
